---
title: "Predicted Heights by Sex"
format: html
execute: 
  echo: false
  warning: false
  message: false
---

## 📊 Statistical Model

We use a **linear regression model** to estimate height differences between male and female recruits.

$$
Y = \beta_0 + \beta_1 X_1 + \cdots + \beta_n X_n + \epsilon
$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$

This model assumes:

- **Y** = outcome variable (height)  
- **X₁, X₂, ..., Xₙ** = predictor variables (e.g., sex)  
- **β₀** = intercept (mean height for reference group)  
- **β₁, ..., βₙ** = effect of each predictor  
- **ε** = error not explained by predictors  

---

## 🧪 Data Generating Mechanism

We model the relationship using:

$$
\hat{\text{height}} = 162.18 + 15.94 \cdot \text{sexMale}
$$

This means males are predicted to be approximately 16 cm taller than females.

---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(easystats)
library(parsnip)
library(marginaleffects)
library(knitr)
```


```{r}
set.seed(10)

x <- nhanes |>
  filter(age >= 18 & age <= 27) |>
  select(height, sex) |>
  drop_na() |>
  slice_sample(n = 50)

```


```{r}
#| cache: true

fit_height <- linear_reg() |>
  fit(height ~ sex, data = x)

tidy(fit_height, conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  kable(
    caption = "Estimates and 95% Confidence Intervals for Parameters  
    Source: NHANES 2009–2011"
  )

```

📈 Predicted Heights by Sex

```{r}
plot_predictions(fit_height, 
                 condition = "sex",
                 draw = FALSE) |> 
  ggplot(aes(x = sex, 
             y = estimate, 
             color = sex)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  size = 1.2, linewidth = 1.5, fatten = 3) +
  scale_color_manual(values = c("Female" = "#E74C3C", "Male" = "#3498DB")) +
  labs(
    title = "Predicted Height for Male and Female Recruits",
    subtitle = "Males are predicted to be ~16 cm taller than females",
    caption = "Source: USMC Simulated Height Data",
    x = "Sex",
    y = "Height (cm)",
    color = "Sex"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

```

📝 **Summary of Analysis**

- Height is an important physical measurement that varies among individuals and may differ by sex.

- Using data from the NHANES survey (ages 18–27), we compare the average height between male and female recruits.

- One limitation is that this sample may not fully represent future recruit populations.

- We model average height — a continuous variable — as a linear function of sex, a binary variable.

✅ Result: The average predicted height for male recruits is about 178 cm, with a 95% confidence interval from 175 to 181 cm.

