---
title: "Untitled"
format: html
execute: 
  echo: false

---

$$
Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon
$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$

This is the general form of a **linear regression model**.

- **Y** is the **outcome variable** we want to predict — in this case, height.
- **X₁, X₂, ..., Xₙ** are the **predictor variables** (also called covariates) like sex or age.
- **β₀** is the **intercept**, the expected value of Y when all X’s are 0.
- **β₁, β₂, ..., βₙ** are the **coefficients** that show how much each predictor contributes to Y.
- **ε** (epsilon) is the **error term**, representing variation not explained by the model. It is assumed to follow a normal distribution with mean 0 and variance σ².

This model helps us understand how different variables are related


with $\epsilon \sim \mathcal{N}(0, \sigma^2)$

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)


```

```{r}
set.seed(10)

x <- nhanes |>
  filter(age >= 18 & age <= 27) |>
  select(height, sex) |>
  drop_na() |>
  slice_sample(n = 50)

```

## 📝 Summary of Analysis

Height is an important physical measurement that varies among individuals and may differ by sex.  
Using data from the **NHANES** survey, which includes a range of physical attributes for individuals aged 18–27, we aim to compare the average height between **male** and **female** recruits.
One potential limitation is that our data may not fully represent the future recruit population, which could bias our height estimates.